Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-08-09 sm.tex
Include code in SM, update schematic
WIP: pulse sequence
Pulse sequence description in SM

\documentclass[aps,twocolumn,secnumarabic,amsmath,amssymb]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}

@@

% mention effects that are included first?

>>>>

\documentclass[aps,secnumarabic,amsmath,amssymb]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{listings}

@@

\section{Cooling sequence}

\subsection{Optical pumping parameters}
All optical pumping pulses has the same length of $40\mu$s
with a $|F=1,m_F=-1\rangle$ scattering rate of $0.14$ MHz
and a $|F=2,m_F=-1\rangle$ scattering rate of $0.39$ MHz.

\subsection{Raman pulse parameters}
Each of the Raman pulse in the cooling sequence is followed immediately by an optical pumping
pulse with the parameters given above.
The parameters for the Raman pulses are different between different groups and are listed below.
The full Rabi frequency is the two-photon Rabi frequency $\Omega$ excluding the matrix element
from wavefunction overlap.
For a Raman pulse with a power ramp,
the full Rabi frequency gives the arithmetics mean over the duration of the pulse.
The power ramp field gives, if any,
the beam (in terms of their corresponding $F$ number)
that ramps with a Blackman profile during the pulse.
\subsubsection{Group 1}
This group is repeated 5 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 2}
This group is repeated 5 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-8&80&$2\pi\times14$&\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-8&80&$2\pi\times14$&\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 3}
This group is repeated 6 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-7&80&$2\pi\times14$&\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 4}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $x$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-5&60&$2\pi\times14$&\\\hline
    $y$&-2&25&$2\pi\times34$&F1\\\hline
    $z$&-6&80&$2\pi\times14$&\\\hline
    $x$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-5&60&$2\pi\times14$&\\\hline
    $y$&-1&21&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 5}
This group is repeated 7 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-5&90&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-5&90&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 6}
This group is repeated 8 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-4&75&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 7}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-3&60&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 8}
This group is repeated 10 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-1&60&$2\pi\times17$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-2&60&$2\pi\times17$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-1&60&$2\pi\times17$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
\subsubsection{Group 9}
This group is repeated 40 times.
\begin{center}
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Axis&Order&Time ($\mu$s)&Full Rabi frequency (kHz)&Power ramp\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $x$&-1&38&$2\pi\times34$&F1\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $y$&-1&25&$2\pi\times34$&F1\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $x$&-1&43&$2\pi\times34$&F1\\\hline
    $z$&-1&70&$2\pi\times9$&F2\\\hline
    $z$&-1&100&$2\pi\times9$&F2\\\hline
    $y$&-1&28&$2\pi\times34$&F1\\\hline
  \end{tabular}
\end{center}
